Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-19 cordillera-cycle.tex
Express all ages as positive numbers.

To reconstruct the successive phases of growth and decay of the last Cordilleran
ice sheet, palaeo-climatic conditions of the last glacial cycle are mimicked
by applying time-dependent temperature offsets derived from multiple
palaeo-temperature proxy records. Each simulation starts from assumed ice-free
conditions at -120\,kyr, and runs to present. These computations were
performed on 16 to 128 cores at the Swedish National Supercomputing Centre.

@@

% fig:deglacshots-grip
\begin{figure*}
  \includegraphics{deglacshots-grip}
  \caption{Snapshots of modelled surface topography (200\,m contours)
           and surface velocity (colour mapping) from the GRIP simulation,
           corresponding to the last glacial ice volume maximum (-19.1 kyr) and
           the last deglaciation.}
  \label{fig:deglacshots-grip}
\end{figure*}

% fig:deglacshots-epica
\begin{figure*}
  \includegraphics{deglacshots-epica}
  \caption{Snapshots of modelled surface topography (200\,m contours)
           and surface velocity (colour mapping) from the EPICA simulation,
           corresponding to the last glacial ice volume maximum (-17.3 kyr) and
           the last deglaciation.}
  \label{fig:deglacshots-epica}
\end{figure*}

>>>>

To reconstruct the successive phases of growth and decay of the last Cordilleran
ice sheet, palaeo-climatic conditions of the last glacial cycle are mimicked
by applying time-dependent temperature offsets derived from multiple
palaeo-temperature proxy records. Each simulation starts from assumed ice-free
conditions at 120\,kyr, and runs to present. These computations were
performed on 16 to 128 cores at the Swedish National Supercomputing Centre.

@@

% fig:deglacshots-grip
\begin{figure*}
  \includegraphics{deglacshots-grip}
  \caption{Snapshots of modelled surface topography (200\,m contours)
           and surface velocity (colour mapping) from the GRIP simulation,
           corresponding to the last glacial ice volume maximum (19.1\,kyr) and
           the last deglaciation.}
  \label{fig:deglacshots-grip}
\end{figure*}

% fig:deglacshots-epica
\begin{figure*}
  \includegraphics{deglacshots-epica}
  \caption{Snapshots of modelled surface topography (200\,m contours)
           and surface velocity (colour mapping) from the EPICA simulation,
           corresponding to the last glacial ice volume maximum (17.3\,kyr) and
           the last deglaciation.}
  \label{fig:deglacshots-epica}
\end{figure*}
